A thesis draft

### 2018-09-14 draft.tex
Talk about requirements and Kubernetes

 This thesis is part of the VIBES project\todo{Talk about VIBES project, add 
some reference, explain what it is.}, where the necessity for better TCP/IP 
transmission through satellite connections is the main requirement. To 
reach this goal, the project specifications suggest to exploit the 5G incoming 
technology and use the NFV-MANO architecture to perform first packets 
elaboration and performance improvment and finally TCP/IP satellite chunk
optimization with the Performance Enhancing Proxy (PEP). The VIBES project 
proposed five technical requirements\todo{Finish list!}:
\begin{itemize}
 \item Analysis of the applicability of current and new Internet protocols in
the proposed VNF-PEP architecture
\end{itemize}

>>>>

 This thesis is part of the VIBES project\todo{Talk about VIBES project, add 
some reference, explain what it is.}, where the necessity for better TCP/IP 
transmission through satellite connections is the main requirement. To 
reach this goal, the project specifications suggest to exploit the 5G incoming 
technology and use the NFV-MANO architecture to perform first packets 
elaboration and performance improvment and finally TCP/IP satellite chunk
optimization with the Performance Enhancing Proxy (PEP). The VIBES project 
proposed five technical requirements:
\begin{enumerate}
 \item Analysis of the applicability of current and new Internet protocols in
the proposed VNF-PEP architecture
 \item Implementation of a VNF-PEP prototype
 \item Building of a PoC test platform
 \item VNF-PEP validation and performance tests on 5G use-cases
 \item Demonstration testbed management
\end{enumerate}

\subsection{VNF-PEP architecture and internet protocols}

The analysis of this topic revealed to be trivial: since internet has many 
different protocols that would become infeasible to support all of them at the 
same time, packet incapsulation revealed to be the solution: every packet 
incoming in the VNFs have been previously incapsulated by the MANO, making the 
whole architecture indipendent from the protocol a particolar data-flux uses. 
To achieve this, TUN/TAP\todo{Find out acronym} interfaces were used to deploy 
a tunnel between VNFs, allowing them to pass packets encapsulated in UDP ones.

\subsection{VNF-PEP prototype}

Since our goal shifted into creating a MANO testbed, our prototype doesn't 
include PEP. The VNF architecture was shaped following the container 
orchestrator we decided to use: Kubernetes.

\subsubsection{About kubernetes}

As already introduced before, Kubernetes is an open source software framework 
specialized in container management and orchestration. Developed by Google in 
??\todo{Find out the actual date} and written in Go, it allows different 
machines (called nodes from now on) to create an abstraction layer and to form a 
cluster where is possible to run Docker containers without brothering about 
hardware constraints. Nodes can have specific roles and specialization, all of 
them managed by one or many master nodes, that actually manage the 
orchestration.
On top of that, Kubernetes astrae from the virtualization in-use, giving the 
possibility to change the virtualization software in use (i.e. from 
Container-based technology to Virtual machine software).
